Insurance choice, decision assistance, and insurer steering

### 2021-03-29 finals/lunch-and-learn/lunch-learn-202103.Rmd
add switching analysis and update slides

@@

>>>>

---
# Analysis of switching

.center[
  ![:scale 50%](../../figures/switching_regression.png)
]

@@

---
# This is preliminary!

.center[
  ![:scale 50%](https://media.giphy.com/media/3o6Yg9rDXHL8Zrdlza/giphy.gif)
]

---
# Agent compensation

.pull-left[
**Compensation schemes**

- Flat commission 
- Fixed amount from <span>&#36;</span>0 to <span>&#36;</span>264

.pull-right[
  ![](flat_comm.jpg)
]

# Agent compensation

.pull-left[
**Compensation schemes**

- Percentage commission
- Percent of annual premium, from 1% to 5%
]

.pull-right[
  ![](perc_comm.jpg)
]

# Agent compensation

.pull-left[
**Compensation schemes**

- Flat commission, from <span>&#36;</span>0 to <span>&#36;</span>264
- Percentage commission, from 1% to 5% of annual premium

.pull-right[
**Sources of variation**

- Insurer
- New enrollee versus renewal
- Network type (e.g., HMO vs PPO)

---
# Quantifying steering effect

**Calculate commission elasticities of demand**

1. Estimate nested logit choice model with commission as covariate
2. Compute commission elasticity (percent change in demand for a 1% increase in commission)

|                | Agent Users   | All Enrollees  |
| -------------- |:-------------:| --------------:|
| Overall        | 11.18         | 5.39           |
| Large Insurers | 11.94         | 5.75           |
| Small Insurers | 6.33          | 3.08           |
